The Rockerverse: Packages and Applications for Containerization with R

### 2020-01-27 manuscript.Rmd
update comments

# inserting a table in the R Journal currently fails
# waiting for new release of articles including this PR to be published: https://github.com/rstudio/rticles/pull/261
# Until then, use remotes::install_github("rstudio/rticles")
requireNamespace("kableExtra")
knitr::kable(tab, format = "latex", escape = FALSE) %>%
  kableExtra::row_spec(0, angle = -90)
```

>>>>

# insert table
requireNamespace("kableExtra")
knitr::kable(tab, format = "latex", escape = FALSE) %>%
  kableExtra::row_spec(0, angle = -90)
```
